Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-12 article.tex
Need to investigate fitness landscape

The human immune system and human pathogen are in an evolutionary
arms race: our immune systems is selected for the detection
of pathogens, whereas pathogens are selected to avoid detection.
From a pathogen's point of view, however, this struggle 
is of only minor importance:
in seasonal influenza, for example, the selection pressure
exerted by the immune system was only limited \cite{han2019individual}
\richel{but this study does not look into the evolution of TMHs}.
In general, on would expect that evolutionary selection is strongest 
for regions that are important for viral proteins' functions:
in COVID-19, for example, there is preliminary evidence that the strongest
selection pressure is upon residues that changes its virulence \cite{velazquez2020positive}
\richel{residue 251 of ORF3a (an ion channel and a 
viroporin, residue is not part of TMH), and position 84 of ORF8 (unknown function)}.
The part of a pathogen's proteome that is essential, 
only accounts for small part of its full proteome.
Also, these essential parts differ widely between pathogens.
Because of this scarcity and variance in targets, 
one expects that the human immune system
is not tailored to detect these sites, 
as hinted by upon by the aforementioned influenza study.

@@

@@

\paragraph{Extracting polypeptides}

\richel{More detail here}.

@@

>>>>

The human immune system and human pathogen are in an evolutionary
arms race: our immune systems is selected for the detection
of pathogens, whereas pathogens are selected to avoid detection.
From a pathogen's point of view, however, this struggle 
is of only minor importance:
in seasonal influenza, for example, the selection pressure
exerted by the immune system was only limited \cite{han2019individual}

In general, on would hope that evolutionary selection results in
an immune system that as most attentive for loci that are
essential for a virus, as these will be most conserved.
In COVID-19, for example, there is preliminary evidence that the strongest
selection pressure is upon residues that changes its 
virulence \cite{velazquez2020positive}.
These loci, however, only account for a small part of a pathogen's proteome.
Additionally, these essential parts differ widely between pathogens.
Because of this scarcity and variance in targets, 
one can imagine that the human immune system 
is not tailored to detect these sites, 
as hinted by upon by the aforementioned influenza study.

@@

\paragraph{Selection needs to be additive}

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, there would be selection for a mutation to lose it.
If there are many, say hundreds, of epitopes, the selection to lose or
gain an epitope is expected to have little effect. The relation
between the fitness of a pathogen and the number of epitopes is unknown.
One could assume a two-state fitness landscape: being
undetected, due to zero epitopes, or being detected, due to one or more
epitopes. Alternatively, one may hypothesize a gradual fitness decrease per
extra epitope.

```
[FIGURE HERE]
```

Would the pathogen have many epitopes, this study needs to 
assume a gradual fitness landscape. Due to this, we did a simple 
exploratory experiment (see 'Fitness landscape'\richel{TODO}) in which
we counted the number of epitopes in COVID-19. Because the number
of epitopes has decreased, we dared to assume a gradual fitness landscape
and to proceed with the full experiment.

@@

\paragraph{Gene prediction}

Proteogenomics is the field dedicated to, among others,
predict the proteins that arise from a DNA 
sequence \cite{nesvizhskii2014proteogenomics}.
For an ab initio gene prediction of a viral genome, 
we searched the literature for the most recent software tool,
which is Vgas (\cite{zhang2019vgas}). In this article, 
Vgas is compared to tools, such as GeneMarkS (\cite{besemer2001genemarks}),
Prodigal (\cite{hyatt2012gene}), GLIMMER (\cite{delcher1999improved}),
RAST \cite{aziz2008rast} and prokka (\cite{seemann2014prokka}).
We picked the FOSS tool that scored best in the (closed source) Vgas
benchmark (\cite{zhang2019vgas}), which is Prodigal.

@@

Tip: see \cite{bar2020sars} for COVID-19 in numbers.
